Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-12-19 rnni_convexity.tex
make it fit on 15 pages

The reason that this example cannot be transferred to $\rnni$ is that additional rank moves are necessary to merge and then split the two caterpillar subtrees.
Similarly to the example in Figure~\ref{fig:NNI_vs_RNNI}, adding rank moves to the shortest $\nni$ path from $T$ to $R$ results in a path that is no longer a shortest $\rnni$ path.
Sorting the two caterpillar subtrees of $T$ and $R$ independently results in a shorter path in $\rnni$.

@@

The question of whether computing $\rnni$ distances is $\np$-hard is still an open problem.

>>>>

The reason this example cannot be transferred to $\rnni$ is that additional rank moves are necessary to merge and then split the two caterpillar subtrees.
Similarly to the example in Figure~\ref{fig:NNI_vs_RNNI}, adding rank moves to the shortest $\nni$ path from $T$ to $R$ results in a path that is no longer a shortest $\rnni$ path.
Sorting the two caterpillar subtrees of $T$ and $R$ independently results in a shorter path in $\rnni$.

@@

The question of whether computing $\rnni$ distances is $\np$-hard is still open.
